Towards Performance-portable Parallel Programming in Computer Science Education

### 2020-01-21 src/1.Introduction.tex
Typo in 1.Introduction

Secondly, we would like to promote Kokkos to students as a platform to understand and experiment with parallel patterns and types. Type specialization through templating allows to experiment with memory layouts and investigate their performance implications. Further, its modular code organization and open access under the BSD license allow students to peak behind the scenes and explore the mappings of abstractions to a variety of vendor-specific implementations. We believe that this makes Kokkos a valuable programming model for students to reason about vendor-provided programming models and to see them as particular implementations of higher abstractions in a parallel programming landscape.

>>>>

Secondly, we would like to promote Kokkos to students as a platform to understand and experiment with parallel patterns and types. Type specialization through templating allows to experiment with memory layouts and investigate their performance implications. Further, its modular code organization and open access under the BSD license allow students to peek behind the scenes and explore the mappings of abstractions to a variety of vendor-specific implementations. We believe that this makes Kokkos a valuable programming model for students to reason about vendor-provided programming models and to see them as particular implementations of higher abstractions in a parallel programming landscape.
